---
title: "The Coindesk Package Explained"
author: "Yifeng Fan"
date: "12/12/2017"
output: rmarkdown::html_vignette
  github_document: default
vignette: >
  %\VignetteIndexEntry{The Coindesk Package Explained}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
The `coindesk` package contains the following functions. All the functions are powered by [CoinDesk](https://www.coindesk.com/price/).

- `bpi_price()` 
- `get_currency_code()` 
- `get_history()`
- `plot_bpi()`


## `bpi_price()` Function
  
The `bpi_price()` function query the current price of BPI. Currency can be specified by adding a list of currency codes. The return dataframe consists of four columns data including currency code, description, float rate and time.

## Example 1: query current BPI 

```{r, message=FALSE, warning=FALSE}
library(coindesk)
library(httr)
library(jsonlite)
# query current Bitcoin Price Index default in USD
bpi_price()
# query current BPI in EUR
bpi_price(currency = 'EUR')
```
This call of the function will return a dataframe consists of BPI in the currency specified by the user (defaul in USD). 

## Example 2: query current BPI in a list of currency
```{r, message=FALSE, warning=FALSE}
library(coindesk)
library(httr)
library(jsonlite)
# query current Bitcoin Price Index in a list of currencies
currency <- c("EUR","CNY","AUD")
bpi_price(currency)
```

This call will return a dataframe consists of BPI in a list of currencies.

## `get_currency_code()` Function

The `get_currency_code()` function is used to show the currency codes used for BPI query. It consists of 167 contries' currency codes.

## Example

```{r, message=FALSE, warning=FALSE}
library(coindesk)
# check and get currency code
currency <- get_currency_code()
# check the first ten currencies
head(currency, 10)
# check the last ten currencies
tail(currency, 10)
# check the number of supported currencies (167 countries in total)
length(currency$currency) 
```

## `get_history()` Function 
This function will return the history BPI. Currency, start date, end date can be specified in the query using parameter `currency`, `start` and `end`. The default currency is USD and the default time duration is last one month. The function will return yesterday's BPI if `yesterday` parameter is set to `TRUE`

## Example 1: query past one month data

```{r, message=FALSE, warning=FALSE}
library(coindesk)
library(httr)
library(jsonlite)
# get past 31 days BPI in CNY
past_month <- get_history(currency = 'CNY')
# check the head of past month data
head(past_month, 10)
# check the tail of past month data
tail(past_month, 10)
# length of the past_month (31 days)
length(past_month$price)
```

## Example 2: query data by specifying date
```{r, message=FALSE, warning=FALSE}
library(coindesk)
library(httr)
library(jsonlite)
# get historical BPI from Oct.1 2017 to Dec.1 2017 in EUR
randomDate <- get_history(currency = 'EUR', start = '2017-10-01', end = '2017-12-01')
# check the head of data selected from random date
head(randomDate, 10)
# check the tail of data selected from random date
tail(randomDate, 10)
```

## Example 3: query yesterday data
```{r, message=FALSE, warning=FALSE}
library(coindesk)
library(httr)
library(jsonlite)
# get yesterday BPI (default in USD)
get_history(yesterday = TRUE)
# get yesterday BPI, in CNY
get_history(currency = 'CNY', yesterday = TRUE)
```


## `plot_bpi()` Function 
This function will plot the historical BPI data. The parameter `df` is the dataframe that returned from the `get_history()` function.

## Example

```{r, fig.align="center", fig.height=4.32, fig.width=7, message=FALSE, warning=FALSE}
library(coindesk)
library(httr)
library(jsonlite)
# get a sample query result from the package 
sample <- coindesk::df
# check the head of sample data in the package
head(sample, 10)
# plot the time and the price of the sample result
plot_bpi(coindesk::df)
```

